---
title: "sec-location"
author: "Chiyoung Ahn and Jasmine Hao"
date: "November 12, 2018"
# output: html_document
output:
  md_document:
    variant: markdown_github
---
# SEC firm locations

This is an example of scraping location information of firms.
The firms uses rvest, for scraping data of a HTML page given the node number.

The doccumentation of R vest file: 
[Rvest Documentation](https://cran.r-project.org/web/packages/rvest/rvest.pdf)


The ggmap is used for extracting the longitude and latitude information given a string containing the address.

The documentation of ggmap: [ggmap Documentation](https://cran.r-project.org/web/packages/ggmap/ggmap.pdf)

Other than that, the natural language processing is done using tm and stringr.

```{r setup, include=TRUE,message=FALSE}
for (pkg in c("rvest","httr","dplyr","stringr","XML","RCurl","ggplot2","reshape","tm","ggmap")){
 if (!pkg %in% rownames(installed.packages())){install.packages(pkg)}
}
library(rvest)
library(dplyr)
library(stringr)
library(ggmap)
library(XML)
library(httr)
library(tm)
```

## Getting firm addresses from SEC website

The SIC code for industries are available for lookup: [SIC](https://www.sec.gov/info/edgar/siccodes.htm) 
Could be intersting industries:
6500:	REAL ESTATE
6798: Real Estate Investment Trusts
7371: Computer Programming Services

We analyze the following industries:
1400:	MINING & QUARRYING OF NONMETALLIC MINERALS (NO FUELS)
5734:	RETAIL-COMPUTER & COMPUTER SOFTWARE STORES
```{r sic-defn}
# SIC.CODES <- c(6798, 7371)
# SIC.NAMES <- c("SIC 6798: Real Estate Investment Trusts","SIC 7371: Computer Programming Services")
SIC.CODES <- c(1400, 5734)
SIC.NAMES <- c("SIC 1400:Mining ","SIC 5734:Retail computer")
```

Define a function that searches all firms in a given industry from the SEC website:
```{r search-firm}
MAX.PAGE <- 1 # maximum number of pages to be read (each page contains 100 firms)

ConstructFirmDF <- function(sic) {
  i <- 0
  continue_indic = TRUE
  firm.df <- data.frame(firm_code=character(),compnay=character(),state=character())
  
  while (continue_indic){
    search_url <- paste('https://www.sec.gov/cgi-bin/browse-edgar?',
                      'action=getcompany&SIC=',sic,
                      '&owner=exclude&match=&start=',i*100,'&count=100&hidefilings=0',
                      sep="")
  
    search_info <- GET(search_url)
    parsed_search <- htmlParse(search_info)
    info <- try( data.frame(readHTMLTable(parsed_search)),TRUE)
    
    i <- i+1
    if (typeof(info) != "list"|| (i > MAX.PAGE) ) {
      break
    }
    names(info) <- c("firm_code","company","state")
    firm.df <- rbind(firm.df,info)
  }
  
  return (firm.df)
}

firm.df.1 <- ConstructFirmDF(SIC.CODES[1])
firm.df.2 <- ConstructFirmDF(SIC.CODES[2])
print(head(firm.df.1))
print(head(firm.df.2))
```

For each individual firm, find the location in the firm's home page.
```{r}
GetLocation <- function(firm_code){
  url <- paste('https://www.sec.gov/cgi-bin/browse-edgar?action=getcompany&CIK=',
               firm_code,'&owner=include&count=40&hidefilings=0',sep = "")
  firm_page <- read_html(url)
  addr_str <- firm_page %>% html_nodes(".mailer") %>% html_text() 
  mail_addr <- addr_str[1] %>% strsplit("\n") 
  mail_addr <- mail_addr[[1]][-1] %>% str_trim() %>% str_c(collapse = "\n")
  
  # The first element is buisness address, the second is the mailing address
  return(mail_addr)
}

firm.df.1$address <- sapply(firm.df.1$firm_code, GetLocation)
firm.df.2$address <- sapply(firm.df.2$firm_code, GetLocation)

print(head(firm.df.1))
print(head(firm.df.2))
```


## Getting location
It turns out that company addresses are not sufficient for plotting -- we need geographical locations in terms of latitude and longitude as well. One good news is that `ggmap` can handle this pretty well. Construct the following function that returns the address given an addresss string:
```{r address-to-location}
GetGeocode <- function (address) {
  geocode(address, source = "dsk") # extract geocode using Data Science Toolkit
}
```

For instance, the geocode of company `BOREALIS TECHNOLOGY CORP` from `https://www.sec.gov/cgi-bin/browse-edgar?action=getcompany&CIK=0001014767&owner=include&count=40&hidefilings=0` can be found by passing their business address:
```{r address-to-location-example}
address <- "4070 SILVER SAGE DR\nSTE 211\nCARSON CITY NV 89701"
GetGeocode(address)
```
where `lon` and `lat` indicate its longitude and latitude respectively.

### Multiple locations
Getting multiple locations can be done by using `lapply` function:
```{r message=FALSE}
firm.df.1.locations <- lapply(firm.df.1$address, GetGeocode)
firm.df.2.locations <- lapply(firm.df.2$address, GetGeocode)
print(head(firm.df.1.locations))
```

Note that some locations might not have been fetched due to errors (some addresses might not exist anymore). `lapply` performs broadcasting a given function (second parameter) to a vector (first parameter) and returns a list, which is why it is called *l*`apply`.

To extract longitudes and latitudes, one can call the followings.
```{r extract-lon-lat}
firm.df.1.lons <- sapply(firm.df.1.locations, "[[", "lon") # extract lon elements from a list of lists
firm.df.1.lats <- sapply(firm.df.1.locations, "[[", "lat") # extract lat elements from a list of lists
firm.df.2.lons <- sapply(firm.df.2.locations, "[[", "lon") # extract lon elements from a list of lists
firm.df.2.lats <- sapply(firm.df.2.locations, "[[", "lat") # extract lat elements from a list of lists
location.df.1 <- data.frame(lon = firm.df.1.lons, lat = firm.df.1.lats)
location.df.2 <- data.frame(lon = firm.df.2.lons, lat = firm.df.2.lats)
```


## Plotting locations
First, construct a combined `data.frame` for plot:

```{r}
location.df.1$SIC <- SIC.NAMES[1]
location.df.2$SIC <- SIC.NAMES[2]

location.df <- rbind(location.df.1, location.df.2)
```

Plot:
```{r plot-locations}
USA.MAP <- map_data("state") # load USA map from ggmap
ggplot(location.df, aes(x=lon, y=lat, color=SIC)) + 
  borders("world", colour="gray50", fill="white") +
  # geom_map(data=USA.MAP, map=USA.MAP, # draw borders based on USA.MAP
  #         aes(long, lat, map_id=region),
  #         color="gray30", fill=NA) +
  geom_point(size=4) +
  labs(x = "Longitude", y = "Latitude", title = "Firm locations") +
  theme_bw() +
    theme(legend.position="bottom")
```
